Distribution-oblivious Programming

### 2019-09-16 pldi/draft.tex
Add notes on intro

@@

>>>>

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  Distributed systems offer notable benefits over centralized systems.
  Reaping these benefits, however, requires developers to develop and deploy
  software in a manner that makes distribution explicit---a process
  that is quite different from how they compose software for centralized
  systems.
% 
  \emph{Light-touch distribution} is a new approach for scaling out distribution-oblivious shell scripts.
  It leverages the fact that 
% introduced as a drop-in replacement of a language runtime's module system, 
  Our \sys prototype shows substantial speedups over 
  as well as the ability to operate on large input sizes, all without
  any developer input.
\end{abstract}

@@

\section{Introduction}

Distributed systems offer significant benefits over their centralized counterparts.
By parallelizing computation they can  
can speed up computations, mitigate resource-exhaustion attacks, improve fault-tolerance, and balance load during spikes.
% offer notable benefits over their centralized counterparts:
%   using partitioning and replication, they can process and store data with increased throughput and fault-tolerance.
Yet, only a minority of developers, employed by the select few companies that deal with massive datasets, have the luxury of engineering software systems with distribution baked in from the start.
The remaining majority starts by developing and deploying software in a centralized manner---that is, \emph{until} there is a significant change of requirements, such as a load increase.

Despite these benefits, the development and deployment of distributed software remains different from and significantly more difficult than its centralized counterpart.
Whereas anyone can stitch together a Bash script to compute on a single machine, 
  % domain-experts routinely glue scripts together to process and share data. % without the help of a computing expert.
   scaling out to multiple computers requires expert labor around ``point'' solutions with expensive setups, restricted programming interfaces, and exorbitant composition costs~\cite{maas2014holistic, schwarzkopf2013dios, andromeda:hotos:2015, jonas2017occupy, varghese2018next, nefele:18}.
Consider the following Unix pipeline featured in Bentley's Programming Pearls column, slightly modified to work on today's Unix.

% \begin{lstlisting}[language=sh,float=h,numbers=none]
% cat doc.ms |                   # print input file
% groff -t -e -mandoc -Tascii |  # remove formatting
% col -bx |                      # remove backspaces 
% tr A-Z a-z |                   # convert to lower case
% tr -d '[:punct:]' |            # remove punctuation
% sort |                         # put words in alphabetical order
% unique |                       # remove duplicate words
% comm -13 /usr/share/dict -     # report words not in dictionary 
% \end{lstlisting}

\begin{lstlisting}[language=sh,float=h,numbers=none]
 cat *.txt |
 tr -cs A-Za-z`\n` |
 tr A-Z a-z |
 sort |
 uniq -c |
 sort -rn |
 head 5 > output.txt
\end{lstlisting}

This pipeline takes an input file (line 1), removes
